Approximation as Differentiation

### 2025-07-10 main/definability.tex
section numbering.
Suggestion to give F a more meaningful name.

\section{Correctness of the Higher-order Interpretation}
\label{sec:definability}

@@

@@

\begin{proof}
  Instantiate \thmref{glr-definability} with
  $F : \Fam(\LatGal) \to \Fam(\MeetSLat \times \JoinSLat^\op)$. By
  \propref{XXX} we know that $F$ preserves finite products and
  coproducts. $\Fam(\LatGal)$ has extensive coproducts because it is
  the free coproduct completion. Thus we get the category $\GLR(F)$ in
  which we can interpret the calculus with the property that this
\end{proof}

>>>>

\section{Correctness of the Higher-Order Interpretation}
\label{sec:definability}

@@

\roly{Clarify $F$ here refers to \propref{ho-embedding} (esp.~as \thmref{glr-definability} quantifies over
arbitrary $F$), perhaps by giving it a more meaningful name}

@@

\begin{proof}
  Instantiate \thmref{glr-definability} with
  $F : \Fam(\LatGal) \to \Fam(\MeetSLat \times \JoinSLat^\op)$. By
  \propref{ho-embedding} we know that $F$ preserves finite products and
  coproducts. $\Fam(\LatGal)$ has extensive coproducts because it is
  the free coproduct completion. Thus we get the category $\GLR(F)$ in
  which we can interpret the calculus with the property that this
\end{proof}
